\textbf{Unshuffling Permutations}

### 2016-04-05 slides/slides.tex
slides LATIN

\usepackage{euler,palatino}
\usepackage{amsmath,amssymb}
\usepackage[utf8]{inputenc}
\usepackage{xxcolor}
\usepackage{graphicx}
\usepackage[ruled]{algorithm2e}
\usepackage[english]{babel}
\usepackage{rotate}
\usepackage{shuffle}
\usepackage{minted}
\usepackage{url}
\usepackage{etoolbox}
\usepackage{tikz}
\usepackage{rotating}
\usetikzlibrary{snakes}
\usetikzlibrary{trees}
\usetikzlibrary{arrows}
\usetikzlibrary{matrix}

@@

@@

\begin{frame}
  \frametitle{Hardness}
  \framesubtitle{Oriented perfect matching}
\end{frame}

>>>>

\usepackage{euler,palatino}
\usepackage{amsmath,amssymb}
\usepackage[utf8]{inputenc}
\usepackage{xxcolor}
\usepackage{graphicx}
\usepackage[ruled]{algorithm2e}
\usepackage[english]{babel}
\usepackage{rotate}
\usepackage{shuffle}
\usepackage{minted}
\usepackage{url}
\usepackage{etoolbox}
\usepackage{tikz}
\usepackage{rotating}
\usetikzlibrary{snakes}
\usetikzlibrary{trees}
\usetikzlibrary{arrows}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}

@@

\newcommand{\MWithContainment}{%
\begin{tikzpicture}[scale=0.1,inner sep=.8pt,node distance=.25cm]
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw (U2.north) .. controls ($ (U2.north) + (0,1.75) $) and ($ (U3.north) + (0,1.75) $) .. (U3.north);
\draw (U1.north) .. controls ($ (U1.north) + (0,2.5) $) and ($ (U4.north) + (0,2.5) $) .. (U4.north);
\end{tikzpicture}
}% end \MWithContainment

\newcommand{\Crossing}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']%,>=stealth',->]
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U3.north) + (0,4) $) .. (U3.north);
\draw [] (U2.north) .. controls ($ (U2.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \Crossing

\newcommand{\LabeledCrossingLL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U3.north) + (0,1.5) $) .. (U3.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \LabeledCrossingLL

\newcommand{\CrossingLL}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']%,>=stealth',->]
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U3.north) + (0,2) $) .. (U3.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\end{tikzpicture}
}% end \CrossingLL

\newcommand{\LabeledCrossingLR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U3.north) + (0,1.5) $) .. (U3.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \LabeledCrossingLR

\newcommand{\CrossingLR}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']%,>=stealth',->]
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U3.north) + (0,4) $) .. (U3.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \CrossingLR

\newcommand{\LabeledCrossingRL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U3.north) + (0,1.5) $) .. (U3.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \LabeledCrossingRL

\newcommand{\CrossingRL}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']%,>=stealth',->]
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U3.north) + (0,4) $) .. (U3.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \CrossingRL

\newcommand{\LabeledCrossingRR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U3.north) + (0,1.5) $) .. (U3.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \LabeledCrossingRR

\newcommand{\CrossingRR}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']%,>=stealth',->]
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U3.north) + (0,4) $) .. (U3.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \CrossingRR

\newcommand{\Inclusion}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\draw [] (U2.north) .. controls ($ (U2.north) + (0,3) $) and ($ (U3.north) + (0,3) $) .. (U3.north);
\end{tikzpicture}
}% end \Inclusion

\newcommand{\LabeledInclusionLL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionLL

\newcommand{\InclusionLL}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
+\draw [->] (U4.north) .. controls ($ (U4.north) + (0,4) $) and ($ (U1.north) + (0,4) $) .. (U1.north);
+\draw [->] (U3.north) .. controls ($ (U3.north) + (0,3) $) and ($ (U2.north) + (0,3) $) .. (U2.north);
\end{tikzpicture}
}% end \InclusionLL

\newcommand{\LabeledInclusionLR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionLR

\newcommand{\InclusionLR}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,3) $) and ($ (U3.north) + (0,3) $) .. (U3.north);
\end{tikzpicture}
}% end \InclusionLR

\newcommand{\LabeledInclusionRL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionRL

\newcommand{\InclusionRL}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,3) $) and ($ (U3.north) + (0,3) $) .. (U3.north);
\end{tikzpicture}
}% end \InclusionRL

\newcommand{\LabeledInclusionRR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionRR

\newcommand{\InclusionRR}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,3) $) and ($ (U3.north) + (0,3) $) .. (U3.north);
\end{tikzpicture}
}% end \InclusionRR

\newcommand{\Precedence}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U2.north) + (0,4) $) .. (U2.north);
\draw [] (U3.north) .. controls ($ (U3.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \Precedence

\newcommand{\LabeledPrecedenceLL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U2.north) + (0,1.5) $) .. (U2.north);
\draw [->] (U3.north) .. controls ($ (U3.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceLL

\newcommand{\PrecedenceLL}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U2.north) + (0,4) $) .. (U2.north);
\draw [->] (U3.north) .. controls ($ (U3.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceLL

\newcommand{\LabeledPrecedenceLR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U2.north) + (0,1.5) $) .. (U2.north);
\draw [<-] (U3.north) .. controls ($ (U3.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceLR

\newcommand{\PrecedenceLR}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U2.north) + (0,4) $) .. (U2.north);
\draw [<-] (U3.north) .. controls ($ (U3.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceLR

\newcommand{\LabeledPrecedenceRL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U2.north) + (0,1.5) $) .. (U2.north);
\draw [->] (U3.north) .. controls ($ (U3.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceRL

\newcommand{\PrecedenceRL}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U2.north) + (0,4) $) .. (U2.north);
\draw [->] (U3.north) .. controls ($ (U3.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceRL

\newcommand{\LabeledPrecedenceRR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex',
                    text height=1.5ex,text depth=.25ex]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U2.north) + (0,1.5) $) .. (U2.north);
\draw [<-] (U3.north) .. controls ($ (U3.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceRR

\newcommand{\PrecedenceRR}{%
\begin{tikzpicture}[yscale=0.08,xscale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U2.north) + (0,4) $) .. (U2.north);
\draw [<-] (U3.north) .. controls ($ (U3.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceRR

@@

\begin{frame}
  \frametitle{Hardness}
  \framesubtitle{Oriented perfect matching}

  \begin{definition}[Property $\mathbf{P_1}$]
    Let $\pi$ be a permutation. An oriented perfect matching $\mathcal{M}$
    on $\pi$ is said to have property $\mathbf{P_1}$ if it avoids all the
    six patterns \InclusionLL, \InclusionLR, \InclusionRL,
    \InclusionRR, \CrossingLR, and \CrossingRL.
  \end{definition}

  \medskip

  \begin{definition}[Property $\mathbf{P_2}$]
    Let $\pi$ be a permutation. An oriented perfect matching $\mathcal{M}$
    on $\pi$ is said to have property $\mathbf{P_2}$ if, for any two
    distinct arcs $(\pi(a), \pi(a'))$ and $(\pi(b), \pi(b'))$ in $\mathcal{M}$,
    we have $\pi(a) < \pi(b)$ if and only if $\pi(a') < \pi(b')$.
  \end{definition}
\end{frame}

\begin{frame}
  \frametitle{Hardness}
  \framesubtitle{Oriented perfect matching}

  \begin{theorem}
    Let $\pi$ be a permutation. The following statements are equivalent:
    \begin{enumerate}
      \item The permutation $\pi$ is a square.
      \item There exists an oriented perfect matching $\mathcal{M}$
      on $\pi$ satisfying~$\mathbf{P_1}$ and~$\mathbf{P_2}$.
    \end{enumerate}
  \end{theorem}

  \medskip

  \onslide<2->
  \begin{exampleblock}{Example}
    \begin{tikzpicture}[scale=0.35,inner sep=2pt,node distance=1cm]
        \draw node [draw,circle,minimum size=.55cm,fill=black!10](U01){$1$};
        \draw node [draw,circle,minimum size=.55cm,fill=black!10,right of=U01]
            (U02) {$8$};
        \draw node [draw,circle,minimum size=.55cm,right of=U02](U03){$3$};
        \draw node [draw,circle,minimum size=.55cm,fill=black!10,right of=U03]
            (U04) {$9$};
        \draw node [draw,circle,minimum size=.55cm,fill=black!10,right of=U04]
            (U05) {$2$};
        \draw node [draw,circle,minimum size=.55cm,right of=U05](U06){$7$};
        \draw node [draw,circle,minimum size=.55cm,right of=U06](U07){$B$};
        \draw node [draw,circle,minimum size=.55cm,right of=U07](U08){$5$};
        \draw node [draw,circle,minimum size=.55cm,right of=U08](U09){$C$};
        \draw node [draw,circle,minimum size=.55cm,right of=U09](U10){$6$};
        \draw node [draw,circle,minimum size=.55cm,fill=black!10,right of=U10]
            (U11) {$A$};
        \draw node [draw,circle,minimum size=.55cm,fill=black!10,right of=U11]
            (U12) {$4$};
        \draw [thick,->,>=latex']
        (U01.north) .. controls ($ (U01.north) + (0,2.25) $)
            and ($ (U03.north) + (0,2.25) $) .. (U03.north);
        \draw [thick,->,>=latex']
        (U02.north) .. controls ($ (U02.north) + (0,2.25) $)
            and ($ (U06.north) + (0,2.25) $) .. (U06.north);
        \draw [thick,->,>=latex']
        (U04.north) .. controls ($ (U04.north) + (0,2.5) $)
            and ($ (U07.north) + (0,2.5) $) .. (U07.north);
        \draw [thick,->,>=latex']
        (U05.north) .. controls ($ (U05.north) + (0,2.5) $)
            and ($ (U08.north) + (0,2.5) $) .. (U08.north);
        \draw [thick,->,>=latex']
        (U11.north) .. controls ($ (U11.north) + (0,2.5) $)
            and ($ (U09.north) + (0,2.5) $) .. (U09.north);
        \draw [thick,->,>=latex']
        (U12.north) .. controls ($ (U12.north) + (0,2.5) $)
            and ($ (U10.north) + (0,2.5) $) .. (U10.north);
    \end{tikzpicture}

    {\small%
    An oriented perfect matching $\mathcal{M}$ on the permutation
    $\pi = 183927B5C6A4$ satisfying the properties $\mathbf{P_1}$
    and $\mathbf{P_2}$. From $\mathcal{M}$, it follows that $\pi$ is
    a square as it appears in the shuffle of $1892A4$ and $37B5C6$,
    both being order-isomorphic to $145263$.
    }%end small
  \end{exampleblock}
\end{frame}
